This R markdown extracts the data for the RTDS 30-day mortality analysis.

It directly reads the SQL file (//filewel01/RTDS/Analytical Work/Sarah Lawton/90 day mortality/Development 2025/CAS2504/Production/1_SQL/RTDS_90DM_CAS2504.sql)

The result of the query is then written to a *.csv file and saved in the Stata directory (//filewel01/RTDS/Analytical Work/Sarah Lawton/90 day mortality/Development 2025/CAS2504/Production/2_Stata/Data)

All of the paths used should be absolute and refer to directories in the RTDS drive on filewel01

#Load packages
```{r setup, include=FALSE}
# Set the correct TIME ZONE, OTHERWISE THERE ARE PROBLEMS WITH DATES
Sys.setenv(TZ='UTC')
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "R:/Analytical work/Sarah Lawton/90 day mortality/Development 2025/CAS2504/Production/1_SQL")
library(readr)
library(readr)
library(tidyverse)
library(rJava)
library(DBI)
library(NDRSAfunctions)
```


#Read Query to send from *.SQL file
```{r, echo=TRUE}

query <- read_file("RTDS_90DM_CAS2504.sql")
query <-  gsub(";", "", query)

```

#Setup CAS connection
```{r, echo=TRUE}
################################################################################

#Set CAS connection details

setwd("R:/Analytical work/Sarah Lawton/90 day mortality/Development 2025/CAS2504/Production/1_SQL/")
snapshot <- "cas2504l"
CAS_user = "analysissarahlawton" #Update this to your CAS username
remotes::install_github(repo = 'NHSE-NDRS/NDRSAfunctions', host = "api.github.com", upgrade = "always", auth_token = Sys.getenv("GH_token"), ref = "HEAD", build_opts=c("--no-lock"), build = FALSE)
#Connect to CAS
cas <- createConnection(username = CAS_user, sid = snapshot, port = 2006)



################################################################################
```


#Run Query 
```{r, echo=TRUE}
## Running the query to get the 30 DM data

query_result <- dbGetQueryOracle(cas, query)
```

#Save Query result to file
```{r, echo=TRUE}
setwd("R:/Analytical work/Sarah Lawton/90 day mortality/Development 2025/CAS2504/Production/2_Stata/Data/")
write_csv(query_result, paste0("RTDS_90DM_CAS2504_", Sys.Date(), ".csv"), na="", append=FALSE, col_names=TRUE)
```

#Close CAS connection
```{r, echo=TRUE}
dbDisconnect(cas)
```

